Making Sense of Tweets: A framework for individualized student research projects

### 2019-09-25 Rmd/abstract.Rmd
deleted first sentences of abstr

Social media platforms have altered communication methods. The tremendous volumes of streaming data that are available through platforms like Twitter and Facebook enable the investigation of new data science research questions. In many cases, these research questions may motivate engaging, accessible, and scientifically meaningful studies for data science research students.
To explore social media data science as a pedagogical tool, we developed a teaching and mentoring framework to guide undergraduate researchers through individualized research projects. We demonstrated our approach by guiding two undergraduate researchers while they completed research projects. Our framework involves research question formulation, data acquisition, data analysis and visualization, and presentation of results. Our two student projects, which serve as case studies for our framework, completed all components of the individualized research projects. We found that research skills, self-confidence in research ability, and professional interest in data science increased for both students. Below, we describe our successes, lessons learned, and ideas for others to build similar frameworks for future honors projects.

>>>>

To explore social media data science as a pedagogical tool, we developed a teaching and mentoring framework to guide undergraduate researchers through individualized research projects. We demonstrated our approach by guiding two undergraduate researchers while they completed research projects. Our framework involves research question formulation, data acquisition, data analysis and visualization, and presentation of results. Our two student projects, which serve as case studies for our framework, completed all components of the individualized research projects. We found that research skills, self-confidence in research ability, and professional interest in data science increased for both students. Below, we describe our successes, lessons learned, and ideas for others to build similar frameworks for future honors projects.
